\documentclass{article}
\usepackage[utf8]{inputenc}

\title{\textbf{FOAR705 Scoping exercise}} 
\author{\textbf{Ellen Kirkpatrick} }
\date{August 2019}

\begin{document}

\maketitle
\section{Research Area}
Great inequality exists in health and welfare outcomes across different population groups in Australia including Indigenous Australians and culturally and linguistically diverse (CALD) groups, despite the institutionalisation of a welfare system. To what extent does the welfare system have its roots in the exclusionary and post-colonial social policies of the early 20th century and has this led to the continual systemic marginalisation of these groups?

\section{Jobs}
I need to develop a methodology for this project and identify the most appropriate research methods in order to collect and analyse data.\\

I need to carry out independent data collection for distinct population groups within Australia including Indigenous Australians and CALD groups. \\

I need to find a program where quantitative and qualitative data sets can be analysed together.\\

I need to review relevant peer-reviewed articles from a range of different  journals and databases. 

\section {Pains}
It will be difficult to find a way to compile data from different levels of government such as state and federal policies, departments and historical developments. Data collection on welfare outcomes is complex due to multiple changes in government departments over the past few decades. This may produce inconsistencies in data collection. \\

There is not much data available on the welfare outcomes of asylum seekers in Australia. Data concerning migrants and the welfare system can also be very vague and ambiguous on demographic details.\\

As the project is so long, it will be difficult to review it and make consistent changes without losing previous work or ideas.\\

It will be difficult to maintain an extensive bibliography list and connect specific references with the appropriate in-text citations as well as ensure it is consistent with the requirements of the Harvard referencing system. \\

I need to appropriately format a large piece of work with hundreds of pages and ensure it is consistent and that it fulfills the appropriate requirements. \\

\section {Pain Relievers}
I need to find a program which can effectively clean, manage and store data so that different data-sets from different time periods can be compiled together. This could be achieved through attending excel workshops or becoming more sufficient in data carpentry.\\

I need to collect my own data and run an analysis in order to work around gaps in the literature. This may require an ethics approval but also knowledge and skills in collecting, analysing and managing data sets. \\

I would like a program or an online platform, such as Github, which allows me to make constant changes to my project without losing copies of previous drafts. It would also need to be stored efficiently as to not take up too much space. \\

I would like a program which stores and manages large bibliography lists more efficiently, such as Microsoft Endnote, and assists in linking them to the appropriate citations within the text. \\

I need a program which makes formatting and managing large files with many pages easier such as Latex. 

\section{Gains}
I would like to become a more competent social scientist through improving my research and analytic skills. \\

I would like to become more efficient in data carpentry in order to spend less time manually managing data when it can be done automatically.\\

I would like to increase my knowledge about back up procedures and different storage options to safeguard my project against technology failures. \\

I would like to be able to successfully draw connections between inequality, welfare outcomes and social policies. 

\section{Gain Creators}
I would carry out practical research in which I will be collect different types of data, run an analysis using different programs and functions and then communicate findings in an academic thesis. \\

I would like to become more familiar with programs such as excel or more sophisticated programs in which data carpentry is required. This will broaden my knowledge and skills in working with data. \\

I would like to find an online storage option which is easy to use in conjunction with other back-up procedures in order to keep my project safe from the chance of technology failure. \\

I would run a comparative analysis on data concerning welfare outcomes. 



\end{document}
